Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

  #brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
  brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)

@@

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = 1500)) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
       xlab("Year") +
       ylab("Title length (words)")
}

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)"))
print(p)
```

>>>>

  brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)

@@

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
       xlab("Decade") +
       ylab("Title length (words)")
}

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) +
      ggtitle(paste("Top publishers in", place, "(", catalogue, ")", sep = ""))
